R Markdown Features

### 2018-10-10 GitHubPage/my_R_book/Rmarkdown_features/rmd_features.rmd
up

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    code_folding: show
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

@@

>>>>

---
title: "R Markdown Features"
subtitle: "A Compact Reference"
author: "[Yongfu Liao](https://liao961120.github.io/)"
date: "`r format(Sys.Date(), '%B %e, %Y')`"
bibliography: /home/liao/local_depend/citation/neanderthals.bib
csl: /home/liao/local_depend/style_sheets/apa.csl
link-citations: yes
output:
  bookdown::html_document2:
    css: /home/liao/local_depend/style_sheets/style.css
    df_print: kable
    toc: true
    toc_depth: 2
    toc_float:
        collapsed: false
---

@@

# Child Documents

It is possible to write R Markdown in separated files and combine them together before knitting to the output file. See [knitr documentation](https://yihui.name/knitr/) for more info.

## Usage

`main.Rmd`:

    ---
    title: "This is Title"
    author: "Yongfu Liao"
    output: html_document
    ---

    `r ''````{r setup}
    options(knitr.duplicate.label = 'allow')
    ```

    `r ''````{r child="part1.Rmd"}
    ```

    `r ''````{r child="part2.Rmd"}
    ```

The skeleton file that combines several R Markdown files. Only this file is rendered, other R Markdown files will automatically be inserted in the knitting process.

To avoid code chunks having the same labels, set the option below in `setup` code chunk of `main.Rmd`.

```r
options(knitr.duplicate.label = 'allow')
```

# Conditional Compilation

```{r eval=FALSE}
if (knitr::is_html_output()) {
  ...
}

if (knitr::opts_knit$get('rmarkdown.pandoc.to') == "latex")
  ...
}
```

@@

# Xaringan (remark.js Slide)

Xaringan is a HTML presentation output format of R Markdown. Xaringan doesn't support Pandoc markdown, but is very flexible and easy to use if having basic CSS knowledge. It also prints well on PDF (using Chrome or [decktape](https://github.com/astefanutti/decktape)). Read the [Chapter 7](https://bookdown.org/yihui/rmarkdown/xaringan.html) of *R Markdown Guide* for more details.

<iframe src="https://liao961120.github.io/slides/xaringan/index.html", width=400, height=301>
</iframe>  
[Slide Link](https://liao961120.github.io/slides/xaringan/index.html)
